A Framework for Equivalence of Cast Calculi and a new Cast Representation

### 2020-10-01 paper.tex
Updates from Overleaf
switched to a bib style that works with author-year
edits and comments in sec 2

% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\usepackage{booktabs}   %% For formal tables:
%% http://ctan.org/pkg/booktabs
%\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
%% http://ctan.org/pkg/subcaption
\usepackage{xcolor} %% For \color
\usepackage{todonotes} %% For \todo
\usepackage{mathtools} %% For \xRightarrow[sub]{sup}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{stmaryrd} %% For \llbracket etc.
\usepackage{semantic}
\usepackage[scaled]{beramono}
\usepackage[T1]{fontenc}
\usepackage[numbers]{natbib} %% For more citation commames (\cite etc.)
\usepackage{listings} %% For typesetting code
\newcommand{\lstsetgrift}{
	\lstset{%
		language=Lisp,%
		basicstyle=\ttfamily\small,%
		keywordstyle=\ttfamily\bfseries\small,%
		columns=flexible,%
		aboveskip=\smallskipamount,%
		belowskip=\smallskipamount,%
		frame=single,%
		xleftmargin=2pt,%
		escapeinside={/+}{+/},%
		mathescape=true,%
		keywords=[1]{define,if,:,Int,Bool,-,=,open},
		literate=%
		{->}{{$\rightarrow$}}2%
		{=>}{{$\Rightarrow$}}2%
		{lambda}{{$\lambda$}}1%
		{→}{{$\rightarrow$ }}2%
		{Γ}{{$\Gamma$ }}1%
		{⊢}{{$\vdash$ }}1%
	}%
}%%
\lstsetgrift

@@

This paper presents a new cast representation named
\emph{hypercoercions}, that is good for both mechanized metatheory and
good for implementation (Section~\ref{sec:hypercoercions}). The
straightforward Agda translation of the composition operator for
hypercoercions is able to pass Agda's termination check and
hypercoercions are suggestive of a bit-level representation that
minimizes the need for pointers and fits all first-order casts into 64
bits.
%
We present two flavors of hypercoercions to support the two blame
tracking strategies from the literature: \LD\ and
\LUD~\citep{siek2009exploring}. With the \LD\ strategy, only 
\textbf{d}own 
casts (casts from \Tdyn\ to some other types) are subject to blame. 
With the 
\LUD\
strategy, however, some \textbf{u}p casts may also be blamed.
We are interested in the D blame
tracking strategy because it comes with a more straightforward notion of
safe cast compared to \LUD~\citep{siek2009exploring}, which is why \LD\ 
was
chosen in the Grift compiler~\citep{kuhlenschmidt2018efficient}. We are also 
interested in \LUD\ because it plays a
prominent role in the gradual typing literature
\citep{wadler2009well}.  The \LUD\ hypercoercions were inspired by the
supercoercions of \citep{Garcia:2013:CTB:2500365.2500603} (hence the name) and
the \LD\ hypercoercions were inspired by the normal forms of
Siek and Garcia~\citep{siek2012interpretations}.
The semantics of casts can be lazy or
eager~\citep{siek2009exploring}. In this paper, we focus on lazy cast
strategies because we suspect that they are more efficient than eager
strategies and because New et al.~\citep{new2019gradual} show that the eager
strategies are incompatible with $\eta$-equivalence of functions.

@@

\todo[inline]{KC: how to make \textbackslash citet work?}
\todo[inline]{JS: Good question! I would like to use citet as well.}

@@

\citet{henglein1994dynamic} introduces coercions to study compilation from 
dynamic languages to static ones. \citet{herman2010space} proposes using 
coercions in normal forms to represent casts in gradual typing and proves space 
efficiency. 
However, they didn't show the coercion-based semantics is equivalent to the 
standard (and type-based) one. \citet{Siek:2015:BCT:2737924.2737968} improves 
the Lazy UD flavor of coercions in normal forms and proves that Lazy UD 
coercions in normal form is correct, using two bisimulation between three 
reduction semantics. The first semantics is similar to \LUDMachine, which 
bisimulates a 
reduction semantics using coercions (not necessarily in normal form). The last 
semantics uses coercions in normal form and bisimulates the coercions-based 
semantics.

@@

\citet{Siek:2010:TWB:1706299.1706342} introduces Lazy UD threesomes and prove 
its correctness, using a bisimulation between two reduction semantics: one is 
similar to \LUDMachine; the other uses Lazy UD threesomes and is similar to the 
machine in Section~\ref{sec:framework}. 
\citet{Garcia:2013:CTB:2500365.2500603} introduces several other flavors of 
threesomes, including a Lazy D one. Their threesomes are derived from 
corresponding flavors of coercions in normal form, using correctness-preserving 
transformation. So the correctness of their threesomes relies on the 
corrections of the coercions-in-normal-form-based semantics defined in 
\citet{herman2010space}, which have not been proved correct.

@@

\citet{garcia2014deriving} presents a dynamic semantics for the Eager D blame 
strategy, using coercions. They claims that "the artefacts for coercions can be
replaced by other artefacts implementing different dynamic semantics".

@@

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\bibliographystyle{splncs04}
\bibliography{bibfile,all-modified}{}

>>>>

% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\usepackage{booktabs}   %% For formal tables:
%% http://ctan.org/pkg/booktabs
%\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
%% http://ctan.org/pkg/subcaption
\usepackage{xcolor} %% For \color
\usepackage{todonotes} %% For \todo
\usepackage{mathtools} %% For \xRightarrow[sub]{sup}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{stmaryrd} %% For \llbracket etc.
\usepackage{semantic}
\usepackage[scaled]{beramono}
\usepackage[T1]{fontenc}
%\usepackage[numbers]{natbib} %% For more citation commames (\cite etc.)
\usepackage{natbib} %% For more citation commames (\cite etc.)
\usepackage{listings} %% For typesetting code
\newcommand{\lstsetgrift}{
	\lstset{%
		language=Lisp,%
		basicstyle=\ttfamily\small,%
		keywordstyle=\ttfamily\bfseries\small,%
		columns=flexible,%
		aboveskip=\smallskipamount,%
		belowskip=\smallskipamount,%
		frame=single,%
		xleftmargin=2pt,%
		escapeinside={/+}{+/},%
		mathescape=true,%
		keywords=[1]{define,if,:,Int,Bool,-,=,open},
		literate=%
		{->}{{$\rightarrow$}}2%
		{=>}{{$\Rightarrow$}}2%
		{lambda}{{$\lambda$}}1%
		{→}{{$\rightarrow$ }}2%
		{Γ}{{$\Gamma$ }}1%
		{⊢}{{$\vdash$ }}1%
	}%
}%%
\lstsetgrift

@@

This paper presents a new cast representation named
\emph{hypercoercions}, that is good for both mechanized metatheory and
good for implementation (Section~\ref{sec:hypercoercions}). The
straightforward Agda translation of the composition operator for
hypercoercions is able to pass Agda's termination check and
hypercoercions are suggestive of a bit-level representation that
minimizes the need for pointers and fits all first-order casts into 64
bits.
%
We present two flavors of hypercoercions to support the two blame
tracking strategies from the literature: \LD\ and
\LUD~\citep{siek2009exploring}. With the \LD\ strategy, only 
\textbf{d}own 
casts (casts from \Tdyn\ to some other types) are subject to blame. 
With the 
\LUD\
strategy, however, some \textbf{u}p casts may also be blamed.
We are interested in the D blame
tracking strategy because it comes with a more straightforward notion of
safe cast compared to \LUD~\citep{siek2009exploring}, which is why \LD\ 
was
chosen in the Grift compiler~\citep{kuhlenschmidt2018efficient}. We are also 
interested in \LUD\ because it plays a
prominent role in the gradual typing literature
\citep{wadler2009well}.  The \LUD\ hypercoercions were inspired by the
supercoercions of \citep{Garcia:2013:CTB:2500365.2500603} (hence the name) and
the \LD\ hypercoercions were inspired by the normal forms of
\citet{siek2012interpretations}.
The semantics of casts can be lazy or
eager~\citep{siek2009exploring}. In this paper, we focus on lazy cast
strategies because we suspect that they are more efficient than eager
strategies and because \citet{new2019gradual} show that the eager
strategies are incompatible with $\eta$-equivalence of functions.

@@

We review closely related work in three areas: coercions in normal
form, threesomes, and parameterized cast calculi.

@@

\citet{henglein1994dynamic} introduces coercions to study compilation
from dynamic languages to statically typed
ones. \citet{herman2010space} proposes using coercions in normal forms
to represent casts in gradual typing and proves space efficiency.
However, they did not prove that the coercion-based semantics is
equivalent to the standard (and type-based)
one. \citet{Siek:2015:BCT:2737924.2737968} improve the Lazy UD style
of coercions in normal forms and prove that Lazy UD coercions in
normal form are correct, using two bisimulation between three
reduction semantics. The first semantics is similar to \LUDMachine,
which bisimulates a reduction semantics using coercions (not
necessarily in normal form). The last semantics uses coercions in
normal form and bisimulates the coercions-based semantics.

\todo[inline]{JS: say something about the difference between the above
  and what is in this paper. That's the whole point of the related work
  section from the eyes of the reviewer.}

@@

\citet{Siek:2010:TWB:1706299.1706342} introduce Lazy UD threesomes and
prove them correct, using a bisimulation between two reduction
semantics: one is analogous to the \LUDMachine; the other uses Lazy UD
threesomes and is analogous to the machine in
Section~\ref{sec:framework}.  \citet{Garcia:2013:CTB:2500365.2500603}
introduces several other flavors of threesomes, including a Lazy D
one. Their threesomes are derived from the corresponding styles of
coercions in normal form, using correctness-preserving
transformation. So the correctness of their threesomes relies on the
correctness of the coercions-in-normal-form-based semantics defined in
\citet{herman2010space}, which has not been proved correct.

\todo[inline]{JS: again, say something about the difference between
  the above and what is in this paper.}

@@

\citet{garcia2014deriving} presents a dynamic semantics for the Eager
D blame strategy, using coercions. They claim that ``the artefacts for
coercions can be replaced by other artefacts implementing different
dynamic semantics''.

\todo[inline]{JS: The above is too short of a description of that related
work.}

@@

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
%\bibliographystyle{splncs04}
\bibliographystyle{splncsnat}
\bibliography{bibfile,all-modified}{}
